---
title: "Investigating the Nanopore fast5 files from Seal MinION run"
output: html_notebook
---

This notebook is for the initial investigation of fast5 files from a MinION run on a grey seal sample that predates my PhD. The data generated hasn't been explored in great detail outside of some exploratory MinKNOW/WIMP. I want to analyse the data in greater detail which will require first investigating the condition of the pass/skip/fail fast5 files generated before rebasecalling all the pass/skip/fail fast5 files on the grufffalo cluster using my own bash scripts and doing further analysis such as BLAST etc.

This notebook is solely for the initial investigation of the pass/skip/fail fast5 files generated. As there are so many fast5 files generated, I have only taken one fast5 file from the first subdirectory of each pass/skip/fail directory


Part One: Installing BiocManager and rhdf5 package (I did this in console as only needed to be installed once)

```{r}
#if (!require("BiocManager", quietly = TRUE))
   # install.packages("BiocManager")
#BiocManager::install(version = "3.14")
#BiocManager::install("rhdf5")
```


r setup means that when you run this scipt in its entirety, the line of code under r setup must run first (for example if you had library function to load in packages etc.)

```{r setup}
library(rhdf5)
```


Loading the data (one fast5 file from the first subdirectory in each pass/skip/fail directory)

```{r loadingdata}
read.
```
